---
title: "Do people watch the news for the news? Or for their confirmation bias?"
author: "Chien-Che Hung"
date: "12/23/2020"
abstract: |
  In this report, we would be discussing the Taiwanese's 
  political behavior with the influence of the Taiwanese 
  television news outlets. In Taiwan, most new outlets 
  would report news in favor of the major political 
  parties, the Democratic Progressive Party (DPP, Green
  Party) and the Chinese Nationalist Party (KMT, Blue 
  Party). Specifically, we want to determine whether 
  people watch the news for political information or 
  their confirmation bias. We utilize the data from 
  Taiwan Communication Survey (TCS) to conduct this 
  analysis.We decide to focus on news from televisions because 
  the respondents believe that television news is 
  more trustworthy than the internet's information. 
  Due to the reason that the response variable that 
  we are using has five categories, "Tsai Ing-wen from 
  the DPP" (GreenParty), "Eric Chu from the KMT" (Blue 
  Party), "James Soong from the PFP" (Neutral Party), 
  "Don'tKnow," and "You would not cast a vote," we would
  be using Multinomial Logistic Regression to find out 
  the relationship between the odds of voting for the 
  candidates and the media behavior. In our analysis, 
  regardless of the party, the respondents initially 
  supported, watching the news from the opposing party
  would change their support parties. We can conclude 
  that even though people support their parties outside 
  the elections, watching the news from different 
  television sources could increase their chances 
  of changing their support to other parties. 

  **Keywords**: Taiwanese Media, Election, Multinomial Logistic Regression
output: 
  pdf_document:
    extra_dependencies: ["dcolumn"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# load the packages that's needed
library(nnet)
library(ggplot2)
library(reshape2)
library(haven)
library(knitr)
library(kableExtra)
library(dplyr)
library(stargazer)
library(car)
library(gridExtra)
# set the digits
options(scipen = 999, digits = 10)
# set the seed for reproducibility
set.seed(123)
```


```{r, include=FALSE}
# codes
# import data sets that we obtained from the data_cleaning file
media <- read.csv("input/media.csv")
media <- media[,-1]
media_all <- read.csv("input/media_all.csv")
media_all <- media_all[,-1]
green <- read.csv("input/green_party.csv")
green <- green[,-1]
blue <- read.csv("input/blue_party.csv")
blue <- blue[,-1]
neutral <- read.csv("input/neutral.csv")
neutral <- neutral[,-1]

# green party model
# change the variables into factors
green$Media_Lean_Obj <- as.factor(green$Media_Lean_Obj)
green$Candidates <- as.factor(green$Candidates)
green$Gender <- as.factor(green$Gender)
green$Education <- as.factor(green$Education)
# set the reference categories
green <- within(green, Media_Lean_Obj <- relevel(Media_Lean_Obj, ref = "Green"))
green <- within(green, Gender <- relevel(Gender, ref = "female"))
green <- within(green, Candidates <- relevel(Candidates, ref = "Tsai Ing-wen from the DPP"))
# fit the model
green_mod <- multinom(formula = Candidates ~ Gender + Age + as.numeric(as.factor(Marital_Status))
                     + as.numeric(as.factor(Education)) + Frequency + Media_Lean_Obj, data = green)
# get the exponentiated coefficients
green_mod_coeff <- as.data.frame(t(exp(coef(green_mod))))

# coefficient checks
green_check_blue <- linearHypothesis(green_mod,
                      c("Eric Chu from the KMT:Media_Lean_ObjBlue = 0"))
green_check_neutral <- linearHypothesis(green_mod,
                      c("James Soong from the PFP:Media_Lean_ObjNeutral = 0"))

# blue model
# make the variables factor
blue$Media_Lean_Obj <- as.factor(blue$Media_Lean_Obj)
blue$Candidates <- as.factor(blue$Candidates)
blue$Gender <- as.factor(blue$Gender)
# set the reference categories
blue <- within(blue, Gender <- relevel(Gender, ref = "female"))
blue <- within(blue, Media_Lean_Obj <- relevel(Media_Lean_Obj, ref = "Blue"))
blue <- within(blue, Candidates <- relevel(Candidates, ref = "Eric Chu from the KMT"))
# fit the multi-nomial model
blue_mod <- multinom(formula = Candidates ~ Gender + Age + as.numeric(as.factor(Marital_Status))
                      + as.numeric(as.factor(Education)) + Frequency + Media_Lean_Obj, data = blue)
# get the exponentiated coefficients
blue_mod_coeff <- as.data.frame(t(exp(coef(blue_mod))))

# lienar hypothesis check
blue_check_green <- linearHypothesis(blue_mod,
                      c("Tsai Ing-wen from the DPP:Media_Lean_ObjGreen = 0"))
blue_check_neutral <- linearHypothesis(blue_mod,
                      c("James Soong from the PFP:Media_Lean_ObjNeutral = 0"))

# neutral
# make the variables as factors
neutral$Media_Lean_Obj <- as.factor(neutral$Media_Lean_Obj)
neutral$Candidates <- as.factor(neutral$Candidates)
neutral$Gender <- as.factor(neutral$Gender)
# set the reference variable
neutral <- within(neutral, Gender <- relevel(Gender, ref = "female"))
neutral <- within(neutral, Media_Lean_Obj <- relevel(Media_Lean_Obj, ref = "Neutral"))
neutral <- within(neutral, Candidates <- relevel(Candidates, ref = "James Soong from the PFP"))
# fit the multi-nomial model
neutral_mod <- multinom(formula = Candidates ~ Gender + Age + as.numeric(as.factor(Marital_Status))
                      + as.numeric(as.factor(Education)) + Frequency + Media_Lean_Obj, data = neutral, model = TRUE)
# exponentiated coefficients
neutral_mod_coeff <- as.data.frame(t(exp(coef(neutral_mod))))

# clienar hypothesis checks
neutral_check_green <- linearHypothesis(neutral_mod,
                      c("Tsai Ing-wen from the DPP:Media_Lean_ObjGreen = 0"))

neutral_check_blue <- linearHypothesis(neutral_mod,
                      c("Eric Chu from the KMT:Media_Lean_ObjBlue = 0"))
```


# Introduction

In Taiwan, television news channels are relatively competitive compared to other channels, such as entertainment channels. Including
paid TV channels and free-to-air TV channels, there are approximately 19 news channels. In the Taiwanese News market, it is believed
that while a small number of channels report news in an objective and neutral sense, the majority of the news channel report news in
favor of either one of the significant Taiwanese political parties, Democratic Progressive Party (DPP) and Chinese Nationalist Party
(KMT). The ideology for DPP is Social Liberalism, whereas KMT's ideologies are Conservatism and Chinese Nationalism. For example, the
news Sanlih E-Television News (SET) and Formosa Television (FTV) reports typically are slanted towards DPP, and the information from
Television Broadcast Satellite (TVBS) is usually slanted towards KMT.

With the apparent stances that these news channels have, this report explores people's behavior of watching the news. For people who
support either DPP or KMT, we want to find out the odds of changing the parties they support in relation to the news outlets they
watch during the 2016 presidential election by analyzing the Taiwan Communication Survey data. The response variable for this
analysis would be the answer to the question of "Suppose that the 2016 presidential election was being held today, which of the
following candidates would you vote for?" Due to the reason that there are five categories in the answer, we are going to use
Multinomial Logistic Regression. It is a method that is similar to Binomial Logistic Regression but for categories in the response
variable that have more than two options. 

Before we apply this model, we will separate the original data into three sub-datasets based on people's parties. After separating
them, we would apply the models. The variables that we are going to use are some demographic variables such as Age, Gender, Education
Level, and Marital Status. The variable related to news outlets would be the frequency of news per day in a week and the political
stances on the information they watch. The variables that will be used would be elaborated clearly in the Data and Model section
below. By applying this model, we can determine how the news outlets affect people's choice in the presidential election. Several
interesting conclusions can be drawn from our analysis. For example, what is the increase in odds of voting for the opposing
candidate that you support? Or what party's supporters have a larger chance of changing their thoughts after including the effect of
news outlet influences.

This report would talk about the analysis being done by introducing the data first. The Data section includes the source of the data,
how the data is collected, and what data manipulation that we did for the model that we are fitting. After the data section, we will
explain and present the model that we are using in this report. Following the Model section, we would demonstrate the model result
and discuss what it means in the discussion section. Finally, we would also talk about what improvements can be made to improve our
analysis.

# Data

## Data Introduction

This data is obtained from the result of the fourth wave Taiwan Communication Survey (TCS) in 2015: Political and Civic
Communication. TCS's aim is to track developments and changes in media behavior in Taiwan. Specifically, this wave of survey focuses
on politics and public affair information dissemination, people's knowledge on politics, and election options and acknowledgment.
There are three common information dissemination methods: interpersonal communication, mass media communication, and new media
communication. Here, new media communication is defined as mass communication using digital technologies such as the internet. 

As we stated in the introduction, we are trying to find whether people obtain information in ways that fit the ideology of the
political party that they support. The main reason why we are focusing on television news outlets is because Taiwan news outlets 
have obvious political parties they support, either DPP or KMT. In addition, from the observation of TCS survey, around 50% of the
interviewers choose to get the latest information from the Internet, whereas 45% of the interviewers would choose to watch 
television for the latest news. However, under the question of which source of information they trust the most, around 60% of the 
interviewers choose the television, whereas only 27% of the interviewers choose the Internet. Because of this reason, news outlet 
television would provide the best explanation on the interviewers' political behaviors to the questions this paper is exploring. The comparison is presented in Figure 1. 

```{r fig.cap= "News source people watch vs News source people trust", echo = FALSE, fig.width = 6, fig.height = 4}
# graph for the source of media
source <- ggplot(media, aes(x = as.factor(h2))) + 
  geom_bar(stat = "count", width = 0.7) +
  ggtitle("Latest News -- News Source") +
  xlab("Media Type") +
  ylab("Count") +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 45, hjust = 1))
# graph of trust of the news source
trust <- ggplot(media, aes(x = as.factor(h2))) + 
  geom_bar(stat = "count", width = 0.7) +
  ggtitle("Trust -- News Source") +
  xlab("Media Type") +
  ylab("Count") +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 45, hjust = 1))
# make them side by side graph 
grid.arrange(source, trust, ncol = 2)
```

\newpage


## Sampling Method

The methodology that TCS used was Stratified Three-Stage Probability Proportional to Size Sampling through Computer Assisted Personal
Interviewing (CAPI) on Commsurvey application. For this survey, the population was people who were eighteen-year-old and above, and
the sample frame was people who lived at their registered residences for at least four days per week on the main island of Taiwan.
The final sample for this survey is the people who got sampled through TCS's sampling method. The first stage was conducting random
sampling on District and Township. Within the District and Township samples, a random sampling method on Urban Villages and Rural
Villages would be conducted. In the third stage, address numbers within the Urban Villages and Rural Villages would be randomly
sampled. For those households being sampled, interviewees would interview the household member within the pre-determined age range.
The age range that was assigned was based on the age distribution of the entire population.

The nonresponse of the survey would occur in the survey. TCS member solved the nonresponse question by contacting the interviewees
directly for their answers if the contact information was available. If the contact information was unavailable, the nonresponse
questions would be filled in by the age-range's average. When there are "other" options in the questions, the reviewer after the
survey was conducted would review the answers and categorize them into a pre-existent answer. If the pre-existent answers could not
fit the the answers in the "other" options and the similar answers appeared several times in from the interviewees, the reviewer
would add an option and categorize their answers in that option.

The noticeable feature from this survey was the well-structured sampling methods that could avoid the imbalanced situation among
cities and townships. In addition, the flow that the questionnaire possessed made the questions easy to answer and the purpose of
the questions were obvious. The intuitiveness not only benefit the goals that they tried to achieve, but also assisted people who
would like to analyze their results. However, the way they conducted error correction could be very subjective. As we mentioned on
how TCS managed to categorize "other" option into pre-existent options or newly-created option, this could really depend on how the
reviewers thought at the moment during the review process. The answers would not be raw enough for the data analysis process. 


## Variables and Data Pre-Processing

Because we are trying to understand the relationship between interviewees' television news channel choices and political choices,
this analysis would include several variables: people's political stances, the news channel they usually watch, the frequency of
watching news, and who they would vote for on the 2016 Presidential Election. Most importantly, we would include interviewees'
demographic variables because demographics could also contribute to who they will vote for during the 2016 Presidential Election.
For example, according to an article from Taipei Times, KMT received no support from the age group of 20-24. This shows that the
importance to include age groups in our analysis. (Chang, 2020)

For converting the data into usable for our models, some variables required some adjustments. Before manipulating other variables,
we needed to discard some observations because they did not receive news from television, which was the observations that answered
zero on the question asking for the days they watch the news on television per day. The following graph (Figure 2) shows the distribution of the Frequency counts. 

```{r fig.cap= "Frequency Distribution", echo = FALSE, fig.width = 4, fig.height = 3}
# assign NA's to 0
media[is.na(media)] <- 0
# plot the frequency of watching tv
ggplot(media, aes(x = as.factor(k2a))) +
  geom_bar(stat = "count") +
  ggtitle("Frequency of Watching Television per Week") +
  xlab("Days") +
  ylab("Count") +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 45, hjust = 1))
```

For the answers to the question "During the 2016 presidential election, which television channel(s) do you watch most frequently for
getting election news?" it allowed more than one choice. To determine whether the interviewees' options on news outlets were KMT
(Blue Party), DPP (Green Party), or Neutral, we assigned each channel with either -1, 1, or 0 according to the news channel's
political stances. After setting them, we would add all the interviewees' options and determine the political views on the media
they watched. For the sums that were larger than 0, we assigned them as "Blue Party" viewers. For the sums that were lower than 0,
we set them as "Green Party" viewers. For the sums that equaled 0, we put them into the "Neutral" category. The count for each cateogry is as what Figure 3 shows. Also, there was a
variable that asked interviewees about their understanding of the channels' political affiliation. However, in this analysis, we
would not be using it because it blurs the questions that we tried to answer in this paper.

```{r fig.cap= "Media Inclination", echo = FALSE, fig.width = 4, fig.height = 3}
# Plot the media inclination 
ggplot(media_all, aes(x = as.factor(Media_Lean_Obj))) +
  geom_bar(stat = "count") +
  ggtitle("Media Inclination After Data Manipulation") +
  xlab("Parties") +
  ylab("Count") +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 45, hjust = 1))
```

Moreover, the survey asked about who the interviewees would support in the 2016 Presidential Election. If the interviewees did not 
know which candidate to support, the following question asked about which candidate they were leaning towards. We combined these two
questions into one to better indicate whom the interviewees were going to support on the election. As we mentioned, this survey also
asked about which political party the interviewees were leaning towards. Since we were only discussing KMT (Blue Party) and DPP
(Green Party), the rest of the party would be put into the "Neutral" category to fit the political stances the news channels have
(Blue, Green, and Neutral). Figure 4 shows the count distribution for each categories.

```{r fig.cap= "Parties that interviewees support", echo = FALSE, fig.width = 4, fig.height = 3}
# plot the party inclination
ggplot(media_all, aes(x = as.factor(Party))) +
  geom_bar(stat = "count") +
  ggtitle("Party Inclination") +
  xlab("Parties") +
  ylab("Count") +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 45, hjust = 1))
```


After categorizing them into three categories based on their political inclination: "Blue", "Green", and "Neutral," we separated
them into three datasets according to their political inclination. The reason for us to separate them into three datasets is mainly
because we can find whom political inclined interviewees and political neutral interviewees would vote for in 2016 election under
the influence of different political views' news outlets. The table below shows the first six elements of the Blue Party Dataset.

```{r, echo = FALSE}
# example table (blue)
blue <- blue %>% select(Candidates, Gender, Age, Marital_Status, Education, Frequency, Media_Lean_Obj)
kable(head(blue), caption = "First six interviewees for Blue Sub-Dataset") %>% kable_styling(font_size = 7)
```


\newpage

# Model

## Model Introduction

This analysis tries to find the effects on interviewees' television news channel choices on the candidate they intended to vote for
during the 2016 election. As we mentioned in the Data section, we separated the data with 2002 variables into three datasets
according to interviewees' political inclination, which is "Blue Party," "Green Party," and "Neutral." The same model would be
applied to these three datasets. Due to the nature of the Candidate variable, which has five categories: "Tsai Ing-wen from the DPP"
(Green Party), "Eric Chu from the KMT" (Blue Party), "James Soong from the PFP" (Neutral Party), "Don't Know," and "You would not
cast a vote," we are going to use Multinomial Logistic Regression. Similar to Binomial Logistic Regression, the response variable's
log-odds are the independent variable's linear combination. The below explanations would briefly introduce logistic regression and
multinomial regression.

$$
\begin{aligned}
\small
log(\frac{P(A)}{1-P(A)}) &= x_0 + \beta_1 x_1 + ...+\beta_n x_n \\
\end{aligned}
$$

In the model above, the equation's left-hand side is the log-odds of the events, which is taking the logarithm of the probability of
Event A happening over the probability of Event B $(1-P(A))$ happening. On the right hand side, $x_0 \dots x_n$ are the observations
for each variable and $\beta_1 \dots \beta_n$ are the coefficients of the logistic regression.

The description above is the explanation of logistic regression. Multinomial regression works similarly, with more than two outcomes. To explain the regression, let us assume three categories in the response variables: Event A, Event B, and Event C. The equations are in the following model. 

$$
\begin{aligned}
\small
log(\frac{P(A)}{P(B)}) &= x_{01} + \beta_{11} x_{11} +\dots +\beta_{n1} x_{n1} \\
log(\frac{P(C)}{P(B)}) &= x_{02} + \beta_{12} x_{12} +\dots +\beta_{n2} x_{n2}
\end{aligned}
$$

The difference is that rather than having $1-P(A)$ on the denominator in the odds function, we would have to decide a base category
that other events would regress against. In this case, $P(B)$ is the base category, and the results of Event A and Event C would be
fitted relative to $P(B)$. Thus, if we have N categories in our response variable, we would have N-1 separate logistic regressions
with distinct coefficients. In the example we are using, there would be two regressions being trained. On the right hand side of the
regressions, $x_{01} \dots x_{n1}$ and $x_{02} \dots x_{n2}$ are the observations according to the regressions being ran. In addition, $\beta_{11} \dots \beta_{n1}$ and $\beta_{12} \dots \beta_{n2}$ are the coefficients of the regressions accordingly.

## Model

Based on the introduction of the model that we are using in the above subsection, we will talk about the models that we are using in
our analysis. Since we separate the original data into three datasets based on the interviewees' parties, we will build models upon
them separately. In general, the response variable would be the Candidate variable. There are five options like we mentioned above:
"Tsai Ing-wen from the DPP" (Green Party), "Eric Chu from the KMT" (Blue Party), "James Soong from the PFP" (Neutral Party), "Don't
Know," and "You would not cast a vote." The categories satisfy the assumption of performing multinomial logistic regression because
it is a categorical variable and has more than two types. The base category we will use in each dataset would be the dataset
political party's candidate. For example, in Green Party's dataset, the base category would be Green Party's candidate Tsai Ing-wen.
By doing this, we can see the performance of the odds based on the base category. From the number of the Candidates variable types,
we can know that we will fit 5-1 = 4 logistic regression with different events on the numerator in the log-odds for each data.

### DPP (Green Party) Dataset
For the Green Party dataset, the base category would be people who would vote for "Tsai Ing-wen from the DPP" in the 2016 
Presidential Election. 

$$
\begin{aligned}
\small
log(\frac{P(KMT)}{P(DPP)}) = & \beta_{01} + \beta_{11} Gender + \beta_{21}Age + \beta_{31} Marital + \beta_{31} Education + \\& \beta_{41}MediaBlue + \beta_{51} MediaNeutral \\
log(\frac{P(Neutral)}{P(DPP)}) = & \beta_{02} + \beta_{12}Gender + \beta_{22}Age + \beta_{32}Marital + \beta_{32}Education + \\& \beta_{42}MediaBlue + \beta_{52}MediaNeutral \\
log(\frac{P(Dont Know)}{P(DPP)}) = & \beta_{03} + \beta_{13}Gender + \beta_{23}Age + \beta_{33}Marital + \beta_{33}Education + \\& \beta_{43}MediaBlue + \beta_{53}MediaNeutral \\
log(\frac{P(NotVoting)}{P(DPP)}) = & \beta_{04} + \beta_{14}Gender + \beta_{24}Age + \beta_{34}Marital + \beta_{34}Education + \\& \beta_{44}MediaBlue + \beta_{54}MediaNeutral
\end{aligned}
$$

As we mentioned, the base category would be DPP, which is the Green Party's official abbreviation. The variables that we will use in
the models are the following: Gender of the interviewees, Age of the interviewees, Marital Status of the interviewees, Education
Level of the interviewees, and the Media Political Inclination status of the interviewees that we created during the data cleaning
process.  In our data, there is actually a variable about what the interviewee thought about the political stances that the news
outlets have. However, to make the result that we have as objective as possible, we choose to use the variable that we created based
purely on the channels they normally watched. Thus, we decided to exclude such variable. 

For the coefficients, $\beta_{0m}$, where $m = 1, 2, 3, 4$, are the intercepts for each logistic regression that we are fitting. For
$\beta_{1m}$, where $m = 1, 2, 3, 4$, are the coefficients for Gender variable. $\beta_{2m}$ , where m = 1, 2, 3, 4, are the
coefficients of the Age variable. $\beta_{3m}$, where m = 1, 2, 3, 4, are the Marital Status Variable coefficients. $\beta_{3m}$ ,
where m = 1, 2, 3, 4, are the coefficients for the Education Level variable. Since we want to understand the effects of the Blue
side of the news outlet and Neutral news outlet on people who support the Green Party's final choice, we make the Green news outle
a reference category. Thus, the coefficients of $\beta_{4m}$ and $\beta_{5m}$ will be presented as odds against Green news outlet
coefficients automatically equal to 1. We can assess the effects of different news outlets' effects on people voting for the
candidates.

### KMT (Blue Party) Dataset
For the Blue Party dataset, the base category would be people who would vote for "Eric Chu from the KMT" in the 2016 Presidential
Election. 

$$
\begin{aligned}
\small
log(\frac{P(DPP)}{P(KMT)}) = & \beta_{01} + \beta_{11}Gender + \beta_{21}Age + \beta_{31}Marital + \beta_{31}Education + \\ & \beta_{41}MediaGreen + \beta_{51}MediaNeutral \\
log(\frac{P(Dont Know)}{P(KMT)}) = & \beta_{03} + \beta_{13}Gender + \beta_{23}Age + \beta_{33}Marital + \beta_{33}Education + \\& \beta_{43}MediaGreen + \beta_{53}MediaNeutral \\
log(\frac{P(NotVoting)}{P(KMT)}) = & \beta_{04} + \beta_{14}Gender + \beta_{24}Age + \beta_{34}Marital + \beta_{34}Education + \\& \beta_{44}MediaGreen + \beta_{54}MediaNeutral \\
log(\frac{P(Neutral)}{P(KMT)}) = & \beta_{02} + \beta_{12}Gender + \beta_{22}Age + \beta_{32}Marital + \beta_{32}Education +\\& \beta_{42}MediaGreen + \beta_{52}MediaNeutral
\end{aligned}
$$

The structure of each logistic regression function is similar to Green Party Multinomial Logistic Regression, including the
coefficients. The only difference would be the MediaGreen variable. The reason for changing __MediaBlue__ to __MediaGreen__ is 
because by doing this, we can find out the effects that Green News Outlets have on the people who support the Blue Party. Thus, the
coefficients, $\beta_{4m}$ where m = 1, 2,3, 4, are the coefficients for the variable MediaGreen.

Due to the reason that we separate the data into three parts, Green, Blue, and Neutral, we also are going to find the effects of the
news outlets have on people who think they are neutral on the political stances.

$$
\begin{aligned}
\small
log(\frac{P(DPP)}{P(Neutral)}) = &\beta_{01} + \beta_{11}Gender + \beta_{21}Age + \beta_{31}Marital + \beta_{31}Education + \\ & \beta_{41}MediaGreen + \beta_{51}MediaBlue \\
log(\frac{P(KMT)}{P(Neutral)}) = &\beta_{02} + \beta_{12}Gender + \beta_{22}Age + \beta_{32}Marital + \beta_{32}Education + \\ & \beta_{42}MediaGreen + \beta_{52}MediaBlue \\
log(\frac{P(Dont Know)}{P(Neutral)}) = &\beta_{03} + \beta_{13}Gender + \beta_{23}Age + \beta_{33}Marital + \beta_{33}Education + \\& \beta_{43}MediaGreen + \beta_{53}MediaBlue \\
log(\frac{P(NotVoting)}{P(Neutral)}) = &\beta_{04} + \beta_{14}Gender + \beta_{24}Age + \beta_{34}Marital + \beta_{34}Education + \\& \beta_{44}MediaGreen + \beta_{54}MediaBlue
\end{aligned}
$$
Similarly, the regression models' structure is similar to the ones that we mentioned above, with the base model being people who
have neutral political stances. The changes made in this model on the Media Political Inclination variable is also similar to Blue
Party Dataset. We change the MediaNeutral to Media Blue because we can easily increase or decrease odds relative to MediaNeutral. We
can see the effects news outlets, either Green news outlets or Blue news outlets, have on Neutral Voters.

The R programming language would run the above models. The primary function would be multinom from the nnet package. Due to the 
reason that multinomial regressions are fitted via neural networks, we can see the convergence situation during the process of 
fitting the models. The above three models converged after 60, 30, and 30 iterations. For the assumptions to fit this model, we need
to make sure the number of the response variable categories is larger than 2. In this case, the number of categories in the response
variable is 5, which passes the assumption test. The second assumption would be the observation has to be independent of each other.
Due to the sampling methods' nature, the sampling methods from the survey collection stage ensure the independence between the
observations. For multinomial logistic model, we normally have to test an assumption called Independence of Irrelevant Alternative 
(IIA). This is an assumption "that when people are asked to choose among a set of alternatives, their odds of choosing A over B 
should not depend on whether some other alternative C is present or absent." (Paul, 2012) However, we would not test it for the 
following reasons. Due to the nature of our Candidate variable, it would be impossible for people to not recognize the presence of 
other candidates during the election. Also, the test created by Hausman and McFadden does not perform well enough in both small 
samples and large samples. Next, we have to check whether the inclusion of the news outlets' inclinations affects the events' 
log-odds to see if modifications on our model are needed. After conducting the Linear Hypothesis Test with linearHypothesis function
in the car package, some coefficients of MediaBlue, MediaGreen, and MediaNeutral reject the null hypothesis of these coefficients 
equal to zero. Thus, we can say that the inclusion of Media Political Inclination is valid, which means that we do not need 
alternative models for our analysis. Not checking other demographic variables is that they could cause minor adverse effects if the 
variables are not included. The following section will present about the results after fitting the model. 

# Result

In this section, we will present the result that we obtain from our model. There would be three results due to the sub-datasets that
we separated. The hat that in the equations  indicates that they are the estimated values from the regressions.

The estimated coefficients and the intercepts are originally in log-odds form. For better interpretation, we take the exponential of
each cells of the tables presented above. As we take exponential for the elements, the left hand side of the model would become
$\frac{\hat{P}(Category)}{\hat{P}(Base Category)}$, which is the odds of "Category" happening. When the exponentiated coefficients
are larger than 1, it means that the "Category" would have higher probability of happening compared to the "Base Category." On the
other hand, if the exponentiated coefficients are smaller than 1, it means that the "Base Category" would have higher chance of
happening.

\newpage

## DPP Result
Firstly, this is the result from Green Party dataset and the below four equations are the estimated model from our model. 

$$
\begin{aligned}
\small
log(\frac{\hat{P}(KMT)}{\hat{P}(DPP)}) = &\hat{\beta}_{01} + \hat{\beta}_{11}Gender + \hat{\beta}_{21}Age + \hat{\beta}_{31}Marital + \hat{\beta}_{31}Education + \\ &\hat{\beta}_{41}MediaBlue + \hat{\beta}_{51}MediaNeutral \\
log(\frac{\hat{P}(Neutral)}{\hat{P}(DPP)}) = & \hat{\beta}_{02} + \hat{\beta}_{12}Gender + \hat{\beta}_{22}Age + \hat{\beta}_{32}Marital + \hat{\beta}_{32}Education + \\& \hat{\beta}_{42}MediaBlue + \hat{\beta}_{52}MediaNeutral \\
log(\frac{\hat{P}(Dont Know)}{\hat{P}(DPP)}) = & \hat{\beta}_{03} + \hat{\beta}_{13}Gender + \hat{\beta}_{23}Age + \hat{\beta}_{33}Marital + \hat{\beta}_{33}Education + \\& \hat{\beta}_{43}MediaBlue + \hat{\beta}_{53}MediaNeutral \\
log(\frac{\hat{P}(NotVoting)}{\hat{P}(DPP)}) = & \hat{\beta}_{04} + \hat{\beta}_{14}Gender + \hat{\beta}_{24}Age + \hat{\beta}_{34}Marital + \hat{\beta}_{34}Education + \\ &\hat{\beta}_{44}MediaBlue + \hat{\beta}_{54}MediaNeutral \\
\end{aligned}
$$

```{r result table, warning=FALSE, results='asis', echo=FALSE}
# green model coefficents
stargazer(green_mod, header=FALSE, type='latex', font.size = "scriptsize", column.sep.width = "-10pt")
```


From the above table, the coefficients are shown in log odds form. We can see that Neutral News outlets variable's effects on voting
for the Blue Party Candidate and Neutral Party Candidate are statistically significant. In this case, statistically significant means that the p-value is smaller than 0.1, 0.05, or 0.01. P-values in simple words means that the null hypothesis is true. Here the null hypothesis would be the coefficient equals to zero. The table below shows the exponentiated form of the coefficients. The results can be interpreted the way that we described above.

```{r, echo = FALSE, fig.width = 6, fig.height = 4}
# green model exp(coefficients)
rownames(green_mod_coeff) <- c("Intercept", "GenderMale", "Age", "Marital Status", "Education", "Frequency", "Media_ObjGreen",
                              "Media_ObjNeutral")
kable(green_mod_coeff, digits = 5, caption = "Exponentiated Coefficients (Odds Form)") %>% kable_styling(font_size = 7)
```

\newpage

## KMT Result

The below models and the table are the results from the Blue Party dataset. 

$$
\begin{aligned}
\small
log(\frac{\hat{P}(DPP)}{\hat{P}(KMT)}) = &\hat{\beta}_{01} + \hat{\beta}_{11}Gender + \hat{\beta}_{21}Age + \hat{\beta}_{31}Marital + \hat{\beta}_{31}Education + \\ & \hat{\beta}_{41}MediaGreen + \hat{\beta}_{51}MediaNeutral \\
log(\frac{\hat{P}(Dont Know)}{\hat{P}(KMT)}) = &\hat{\beta}_{03} + \hat{\beta}_{13}Gender + \hat{\beta}_{23}Age + \hat{\beta}_{33}Marital + \\&\hat{\beta}_{33}Education + \hat{\beta}_{43}MediaGreen + \hat{\beta}_{53}MediaNeutral \\
log(\frac{\hat{P}(NotVoting)}{\hat{P}(KMT)}) = &\hat{\beta}_{04} + \hat{\beta}_{14}Gender + \hat{\beta}_{24}Age + \hat{\beta}_{34}Marital + \\&\hat{\beta}_{34}Education + \hat{\beta}_{44}MediaGreen + \hat{\beta}_{54}MediaNeutral \\
log(\frac{\hat{P}(Neutral)}{\hat{P}(KMT)}) = &\hat{\beta}_{02} + \hat{\beta}_{12}Gender + \hat{\beta}_{22}Age + \hat{\beta}_{32}Marital + \\& \hat{\beta}_{32}Education + \hat{\beta}_{42}MediaGreen + \hat{\beta}_{52}MediaNeutral \\
\end{aligned}
$$

```{r table, results='asis', echo = FALSE}
# blue model coefficents
stargazer(blue_mod,header=FALSE, type='latex', font.size = "scriptsize", column.sep.width = "-10pt")
```

The estimated coefficients above are also shown in log-odds form. We can see that coefficients of the news outlets who support Green
party have an effect on people who support Blue party's choice on voting for the presidential candidate. Also neutral news outlets'
coefficient is also statistically significant in neutral candidate's model. The table below also shows the exponentiated form of the
coefficients.

```{r, echo = FALSE, fig.width = 6, fig.height = 4}
# blue model exp(coeff)
rownames(blue_mod_coeff) <- c("Intercept", "GenderMale", "Age", "Marital Status", "Education", "Frequency", "Media_ObjGreen",
                              "Media_ObjNeutral")
kable(blue_mod_coeff, digits = 5, caption = "Exponentiated Coefficients (Odds Form)") %>% kable_styling(font_size = 7)
```

\newpage

## Neutral Data

Other than assess the results from the Green Party and Blue Party dataset, we are also going to see the result from the Neutral 
dataset.

$$
\begin{aligned}
\small
log(\frac{\hat{P}(DPP)}{\hat{P}(Neutral)}) = &\hat{\beta}_{01} + \hat{\beta}_{11}Gender + \hat{\beta}_{21}Age + \hat{\beta}_{31}Marital + \hat{\beta}_{31}Education + \\ & \hat{\beta}_{41}MediaGreen + \hat{\beta}_{51}MediaBlue \\
log(\frac{\hat{P}(KMT)}{\hat{P}(Neutral)}) = &\hat{\beta}_{02} + \hat{\beta}_{12}Gender + \hat{\beta}_{22}Age + \hat{\beta}_{32}Marital + \hat{\beta}_{32}Education + \\ &\hat{\beta}_{42}MediaGreen + \hat{\beta}_{52}MediaBlue \\
log(\frac{\hat{P}(Dont Know)}{\hat{P}(Neutral)}) = &\hat{\beta}_{03} + \hat{\beta}_{13}Gender + \hat{\beta}_{23}Age + \hat{\beta}_{33}Marital + \hat{\beta}_{33}Education + \\ & \hat{\beta}_{43}MediaGreen + \hat{\beta}_{53}MediaBlue \\
log(\frac{\hat{P}(NotVoting)}{\hat{P}(Neutral)}) = & \hat{\beta}_{04} + \hat{\beta}_{14}Gender + \hat{\beta}_{24}Age + \hat{\beta}_{34}Marital + \hat{\beta}_{34}Education + \\ & \hat{\beta}_{44}MediaGreen + \hat{\beta}_{54}MediaBlue
\end{aligned}
$$
```{r, results='asis', echo = FALSE}
# neutral model coeff
stargazer::stargazer(neutral_mod,  header=FALSE, type='latex', font.size = "scriptsize", column.sep.width = "-10pt")
```

The table above shows the log-odds results from the model and the table below shows the exponentiated form of the coefficients.

```{r, echo = FALSE, fig.width = 6, fig.height = 4}
# neutral model exp(coeff)
rownames(neutral_mod_coeff) <- c("Intercept", "GenderMale", "Age", "Marital Status", "Education", "Frequency", "Media_ObjGreen",
                              "Media_ObjNeutral")
kable(neutral_mod_coeff, digits = 5, caption = "Exponentiated Coefficients (Odds Form)") %>% kable_styling(font_size = 7)
```

In the Discussion section below, we will discuss the result we just presented above. 

\newpage

# Discussion

This section will talk and discuss the result that we obtained that we presented in the above section. However, the outcome we are
talking about here only speaks to the relationship between the media's stances and the interviewee's ideologies. It does not imply
causation. We will discuss this section by explaining each sub-dataset model and what it means as a whole. After that, we propose
what changes can be made to improve this analysis and apply the result for future use.

## DPP dataset (Table 5)
Like what we mentioned in the Model section, the model category is "Tsai Ing-wen from the DPP." Thus, the results are shown in the
form of log-odds. In order words, the numbers represent how other political stances' media would affect the interviewees to vote for
those parties' candidates. Also, this sub-dataset contains all the interviewees who support the Green Party. In Table 5, we can
see that people who watch news channels that favor Blue Party are five times more likely to vote for the candidate of the Blue Party
— Eric Chu after switching from watching news outlets that support the Green Party. Here, you would not see the odds coefficients
for the Media_Lean_ObjGreen because it is the baseline category. For Neutral Candidate, James Soong from the PFP, the probability
for voting for him is significantly lower than voting for Tsai Ing-wen from the DPP, for both people who watch news that favor the
Blue Party or the Neutral Party. This also means that the interviewees would still support the Green Party's candidate. However, we
can see that switching to watching the news from opposite parties or neutral stances would increase the odds of not voting or do not
who to vote for. In other words, by switching to the news outlets to Blue Parties or Neutral, it would be less likely for the
interviewees to decide who to vote for in the 2016 presidential election.

Let's also examine what other demographics would affect the voting odds for the Blue Party Candidate Eric Chu. The noticeable would
be the frequency. The considerable number indicates that the increase in the frequency of watching the news per week would vastly
increase the odds for voting for the Blue Party's Candidate. From the Gender variable, we can see that the Male interviewees would
be more likely to vote for the candidates from the Blue Party and the Neutral Party, and Female interviewees would be more likely to
choose not to vote or do not know who to vote for.

## KMT dataset (Table 7)

The interpretation would be the same as the DPP dataset. From Table 7 above, people who support the Blue Party and watching Green
Party sided news are four times more likely to vote for Green Party's Candidate — Tsai Ing-wen. Eric Chu from the KMT is not shown
because it is the base category of this model, which means it is the odds function's denominator. Even for Blue Party's supporters
who watch the neutral news would have a higher odds (also higher probability) of voting for Tsai Ing-wen. When we look at the odds
of voting for James Soong from the PFP against Eric Chu from the KMT, for the blue party supporters, it is three times likely for
them to change their minds and vote for Jame Soong if they watch the news outlets in favor of the Green Party. It is also two times
more likely for people to support James Soong if they watch neutral news. However, watching the news that favors the Green Party
would not increase the probability of making people choose not to know who to vote for and not cast a vote. On the other hand, if
people who support Blue Party watch neutral news, it is 95% more likely to answer and do not know how to vote for and 43% more
likely not to vote. In general, we can say that Blue party supporters are more likely to base on the news and understand the news's
facts to choose the people they are going to vote for.

Similar to the DPP dataset, let us take a look at how demographics affect the voting odds. For the Age coefficients, we can see that
the odds are almost equal to 1, which means that the one unit of increase in age only has a small effect on the odds of voting for
the respective candidates, not going to answer do not know. Also, the increased frequency of watching the news per week would
slightly affect the interviewees' choice.

## Neutral Dataset (Table 9)

In this dataset, people selected that they are neutral in their political position. Thus, the model result would show how much and 
how likely the Taiwanese media would affect its citizens' choice of candidates. In Table XXX, for people who watch news outlets that
favor the Blue Party, the odds of voting for Eric Chu from the KMT would double and only slightly affect other candidates. Also, for
people who watch news outlets that favor the Green Party, it would increase the odds of voting for Tsai Ing-wen by 70%, whereas
voting for other candidates would only affect voting. From this result, we can objectively say that there is a relationship between
how media would affect people's decisions even though they have their political position.

For the demographics, we can see that female interviewees have higher odds of voting for the neutral candidate — James Soong. We can
see this from checking out the result table. From Table XXX, we can see that the odds for voting for males decrease around 50% for
voting for other candidates or choosing "don't know" or not casting a vote. We can also see that the increase in frequency does not
affect the odds of voting for any candidates.

## Conclusion

After discussing the three sub-datasets we separated from the primary dataset based on the parties the interviewees support, there
are several conclusions we can imply. However, this analysis only focuses on the relationship between the media and th
interviewees' voting decisions, rather than causation. Firstly, people watching the news from opposite news sources would affect
their candidate choice. We have shown it through the result of our models above. If we only consider the Blue Party and the Green
Party, the Blue Parties' supporters are more likely to change their minds based on the news outlets they watch. If we interpret the
result in this way, it means that for Green supporters, more people strongly believe in the Green Party's ideology and would be less
affected by the information from the media. To conclude the question that we mentioned in the Introduction section: whether people
watch the news or the parties, they support confirmation bias. Based on this analysis, the result would be people do watch the news
for the information and support the candidates that fit their ideology rather than support the candidates only for the party.

There are some improvements and space for future work available for this work. Most importantly, the sample size would be a concern.
Since we separated this data into three datasets based on the parties they support, the dataset with 2002 observations was divided
into three small datasets. The better way to do this would be to have a survey dedicated to this research and sample by cluster
sampling based on the party people support. Another concern of this analysis would be the way we decide the media inclination of the
interviewees. Even though there is a question in the survey asking which party do the news channels that the interviewees watch
support, the reason for not using it is because of the concern of the result being subject and would affect our interpretation's
accuracy. Thus, a potential solution for this concern would be changing the levels that we assigned to the interviewees into
different inclination levels rather than only Green, Blue, and Neutral. By doing this, we believe that we can obtain more insight
from this analysis.


# References

## Data and Literature References

- Joe Bruin. 2006. newtest: command to compute new test.  UCLA:  
Statistical Consulting Group.  https://stats.idre.ucla.edu/stata/ado/analysis/.

- Chang (2020, July 04). KMT lacks message appealing to young voters. Retrieved December 22, 2020, from https://www.taipeitimes.com/News/editorials/archives/2020/07/05/2003739368

- Ching-Ching Chang (2020). The 2015 Taiwan Communication Survey (Phase One, Year Four): Political and Civic Communication (D00161) [data file]. Available from Survey Research Data Archive, Academia Sinica. doi:10.6141/TW-SRDA-D00161-1

- Paul Allison. (2012, October 8). How Relevant is the Independence of Irrelevant Alternatives? Retrieved December 22, 2020, from https://statisticalhorizons.com/iia



## Library References

- Baptiste Auguie (2017). gridExtra: Miscellaneous Functions for "Grid" Graphics. R package
  version 2.3. https://CRAN.R-project.org/package=gridExtra

- Hao Zhu (2020). kableExtra: Construct Complex Table with 'kable' and Pipe Syntax. R package version 1.2.1.
  https://CRAN.R-project.org/package=kableExtra

- Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2020). dplyr: A Grammar of Data Manipulation. R
  package version 1.0.2. https://CRAN.R-project.org/package=dplyr

- Hadley Wickham and Evan Miller (2020). haven: Import and Export 'SPSS', 'Stata' and 'SAS' Files. R package version
  2.3.1. https://CRAN.R-project.org/package=haven

- Hadley Wickham (2016). ggplot2: Elegant Graphics for Data Analysi. Springer-Verlag New York

- JJ Allaire and Yihui Xie and Jonathan McPherson and Javier Luraschi and Kevin Ushey and Aron
  Atkins and Hadley Wickham and Joe Cheng and Winston Chang and Richard Iannone (2020).
  rmarkdown: Dynamic Documents for R. R package version 2.3. URL
  https://rmarkdown.rstudio.com.

- Hadley Wickham (2007). Reshaping Data with the reshape Package. Journal of Statistical
  Software, 21(12), 1-20. URL http://www.jstatsoft.org/v21/i12/.
  
- John Fox and Sanford Weisberg (2019). An {R} Companion to Applied Regression, Third Edition. Thousand Oaks CA: Sage.
  URL: https://socialsciences.mcmaster.ca/jfox/Books/Companion/

- Marek Hlavac (2018). stargazer: Well-Formatted Regression and Summary Statistics Tables. R package version 5.2.1.
  https://CRAN.R-project.org/package=stargazer

- R Core Team (2020). R: A language and environment for statistical computing. R Foundation
  for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.

- Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43),
  1686, https://doi.org/10.21105/joss.01686
  
- Yihui Xie (2020). knitr: A General-Purpose Package for Dynamic Report Generation in R. R
  package version 1.29.
  
# Appendix
- The following link is the github repository for this report: https://github.com/frankkhung/final_project
  